---
title: "Style growth models"
output: html_notebook
---

```{r}
library(tidyverse)
library(skimr)
library(brms)
```

## Data import and wrangle

```{r}
style <- read_csv("../input/Styleelongation2017_ZTslh.csv") %>%
  complete(day, floret, treatment, time)
```
```{r}
style <- style %>% rename(trt=treatment, length=`length (mm)`) %>%
  mutate(hour=as.numeric(time-min(time)) / 3600,  # elapsed hours, first hour = 0
         id=str_c(floret,day,trt,sep="-"))  # unique id for each floret
style %>% mutate(trt=as.factor(trt)) %>% skim()
unique(style$trt)
```

Plot to see what we have:
```{r}
style %>%
  ggplot(aes(x=time, y=length, color=trt, shape=as.character(floret))) +
  geom_point() +
  facet_wrap(~day)
```

remove a few missing data rows that are not at the end of the series
```{r}
style <- style %>% filter(day!=1 | floret!=3 | trt!="East" | hour!=3.5) %>%
  filter(!(is.na(length) & hour < 2))
```

Fix height to max height.  This is necessary because our growth model can't account for shrinkage after reaching max height.  Fill in missing end-of-series values, but note that they are censored.
```{r}
style <- style %>% 
  mutate(censored = ifelse(is.na(length), "right", "none")) %>%
  group_by(id) %>%
  arrange(hour) %>% 
  mutate(length2=ifelse((length < max(length, na.rm = TRUE) | is.na(length)) & row_number() > which.max(length),
                       max(length, na.rm = TRUE), length)) %>%
  ungroup() %>%
  filter(!is.na(length2))
```

Plot smoothed data
```{r}
style %>%
  ggplot(aes(x=time, y=length2, color=trt)) +
  geom_smooth() +
  facet_wrap(~day)
```

And plot averaged over days:
```{r}
style %>%
  ggplot(aes(x=time, y=length2, color=trt)) +
  geom_smooth()
```

### prior predictions

To help figure out reasonable priors

```{r}
weibull <- function(Lmin, Lmax, k, delta, hour) {
  y <- Lmax - (Lmax - Lmin) * exp(-(k*hour)^delta)
  tibble(hour=hour, y=y)
}
```

set up tibble with some priors

```{r}
x <- seq(0,1,.01)
plot(x, dexp(x,1), type = "l")
```

k only 
```{r}
tibble(
  Lmin=7.5,#rnorm(50, 7.5, 1),
  Lmax=11.5,#rnorm(50, 11.5, 1),
  k=rexp(50,1),
  delta=1) %>% #rnorm(50,1,.5)) %>%
  mutate(delta=ifelse(delta < 0, 0, delta)) %>%
  
  mutate(prediction=pmap(list(Lmin, Lmax, k, delta), weibull, seq(0,4.5,.1) ),
         sample=row_number()) %>%
  unnest(prediction) %>%

  ggplot(aes(x=hour,y=y, group=sample)) +
  geom_line(alpha=.2)
```
delta only
```{r}
tibble(
  Lmin=7.5,#rnorm(50, 7.5, 1),
  Lmax=11.5,#rnorm(50, 11.5, 1),
  k=.5,
  delta=rexp(50,.5)) %>%
  mutate(prediction=pmap(list(Lmin, Lmax, k, delta), weibull, seq(0,4.5,.1) ),
         sample=row_number()) %>%
  unnest(prediction) %>%

  ggplot(aes(x=hour,y=y, group=sample)) +
  geom_line(alpha=.2)
```

delta and k
```{r}
tibble(
  Lmin=7.5,#rnorm(50, 7.5, 1),
  Lmax=11.5,#rnorm(50, 11.5, 1),
  k=rexp(100, 1),
  delta=rexp(100,.5)) %>%
  mutate(prediction=pmap(list(Lmin, Lmax, k, delta), weibull, seq(0,4.5,.1) ),
         sample=row_number()) %>%
  unnest(prediction) %>%

  ggplot(aes(x=hour,y=y, group=sample)) +
  geom_line(alpha=.2)
```

all together
```{r}
tibble(
  Lmin=rnorm(100, 7.5, .25),
  Lmax=rnorm(100, 11.5, .25),
  k=rexp(100, 1),
  delta=rexp(100, 0.5)) %>%
  mutate(prediction=pmap(list(Lmin, Lmax, k, delta), weibull, seq(0,4.5,.1) ),
         sample=row_number()) %>%
  unnest(prediction) %>%

  ggplot(aes(x=hour,y=y, group=sample)) +
  geom_line(alpha=.2)
```

# models

## priors

what priors are available to be set?

```{r}
get_prior(bf(
    length2 | cens(censored) ~ Lmax - (Lmax - Lmin) * exp(-(k*hour)^delta), #Weibull model
    Lmax + Lmin ~ 1, 
    delta + k ~ trt + (1|id),
    nl=TRUE ),
  data=style)
```

## minimal 

```{r}
prior1 <- c(prior(normal(7.5,.25), nlpar="Lmin"),
            prior(normal(11.5, .25),nlpar="Lmax"),
            prior(exponential(1),nlpar="k", lb=0),
            prior(exponential(.5),nlpar="delta", lb=0) # 1 is exponential model
)

fit1c <- brm(
  formula=bf(
    length2 | cens(censored) ~ Lmax - (Lmax - Lmin) * exp(-(k*hour)^delta), #Weibull model
    Lmax + Lmin + k + delta ~ 1, #minimal model, parameters do not vary for treatment or random effects
    nl=TRUE),
  data=style,
  prior=prior1,
  sample_prior = "yes",
  cores=4,
  chains=4)
gc()
fit1c <- add_criterion(fit1c, "loo")
```


```{r}
summary(fit1c)
gc()
```

```{r}
plot(fit1c)
gc()
```

```{r}
pairs(fit1c)
gc()
```

```{r}
pred1c <- predict(fit1c)
gc()
```

```{r}
pred1c <- cbind(pred1c, style)

pred1c %>% ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_smooth(span=1) +
  geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_line(aes(y=Estimate),color="yellow") 
```

```{r}
pp_check(fit1c)
```

## fit2c:

```{r, eval=TRUE}

prior2 <- c(prior(normal(7.5,.25), nlpar="Lmin"),
            prior(normal(11.5, .25),nlpar="Lmax"),
            prior(exponential(1),nlpar="k", lb=0),
            prior(exponential(0.5),nlpar="delta"), # 1 is exponential model
            prior(normal(0,0.5), nlpar="delta", coef="trtWest"),
            prior(normal(0,0.5), nlpar="delta", coef="trtWestHeat")
)

fit2c <- brm( # ignore the warning about lower bounds.  If we set it for the intercept, it impacts the other delta coefficients and we don't want that.
  formula=bf(
    length2 | cens(censored) ~ Lmax - (Lmax - Lmin) * exp(-(k*hour)^delta), #Weibull model
    Lmax + Lmin + k ~ 1, 
    delta ~ trt + (1|id),   # 
    nl=TRUE ),
  data=style,
  prior=prior2,
  sample_prior = "yes",
  cores=4,
  chains=4,
  iter=5000 #,
  #control=list(adapt_delta=0.9)
  )

fit2c <- add_criterion(fit2c, "loo")

gc()
```

```{r}
summary(fit2c)
gc()
```


```{r, fig.height=10}
plot(fit2c, ask = FALSE)
gc()
```

```{r}
plot(conditional_effects(fit2c), ask=FALSE)
pp_check(fit2c)
```

```{r}
pred2c <- predict(fit2c)
pred2c %>%
  cbind(style) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_smooth(span=1) +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_smooth(aes(y=Estimate), lty=2, span=1) 
```

```{r}
pred2c %>%
  cbind(style) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_smooth(span=1) +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_smooth(aes(y=Estimate), lty=2, span=1)  +
  facet_wrap(~day, scales = "free_y")
```


```{r}
pred2c %>%
  cbind(style) %>%
  group_by(day, trt, hour) %>%
  summarize(length2 = mean(length2),
            Estimate = mean(Estimate)) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_point() +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_line(aes(y=Estimate), lty=2) +
  facet_wrap(~day, scales = "free_y")
```

```{r}
loo_compare(fit1c, fit2c)
```

Fit2c is preferred, but predictions are not that good relative to observed

```{r}
hypothesis(fit2c, c("delta_trtWest  = 0",
                    "delta_trtWestHeat = 0",
                    "delta_trtWest = delta_trtWestHeat"))
```

## fit3c:

```{r, eval=TRUE}
inits3 <- function() { list(
  b_Lmax=rnorm(1, 11.5, .25),
  b_Lmin=rnorm(1, 7.5, .25),
  b_delta=rexp(1, .5),
  b_k=c(rexp(1, 1), 0, 0),
  z_1=array(0, dim=c(72,1362))
)
}

prior3 <- c(prior(normal(7.5,.25), nlpar="Lmin"),
            prior(normal(11.5, .25),nlpar="Lmax"),
            prior(exponential(1),nlpar="k"),
            prior(normal(0,0.02), nlpar="k", coef="trtWest"),
            prior(normal(0,0.02), nlpar="k", coef="trtWestHeat"),
            prior(exponential(0.5),nlpar="delta") 
)

fit3c <- brm( # ignore the warning about k. 
  formula=bf(
    length2 | cens(censored) ~ Lmax - (Lmax - Lmin) * exp(-(k*hour)^delta), #Weibull model
    Lmax + Lmin + delta ~ 1, 
    k ~ trt + (1|id),   # 
    nl=TRUE ),
  data=style,
  prior=prior3,
  sample_prior = "yes",
  inits = inits3,
  cores=4,
  chains=4,
  iter=5000,
  control=list(adapt_delta=0.99)
  )

fit3c <- add_criterion(fit3c, "loo")

gc()
```

```{r}
summary(fit3c)
gc()
```

```{r}
pairs(fit3c, pars="^b_")
```


```{r, fig.height=10}
plot(fit3c, ask = FALSE)
gc()
```

```{r}
plot(conditional_effects(fit3c), ask=FALSE)
pp_check(fit3c)
```

```{r}
pred3c <- predict(fit3c)
pred3c %>%
  cbind(style) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_smooth(span=1) +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_smooth(aes(y=Estimate), lty=2, span=1) 
```

```{r}
pred3c %>%
  cbind(style) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_smooth(span=1) +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_smooth(aes(y=Estimate), lty=2, span=1)  +
  facet_wrap(~day, scales = "free_y")
```


```{r}
pred3c %>%
  cbind(style) %>%
  group_by(day, trt, hour) %>%
  summarize(length2 = mean(length2),
            Estimate = mean(Estimate)) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_point() +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_line(aes(y=Estimate), lty=2) +
  facet_wrap(~day, scales = "free_y")
```

```{r}
loo_compare(fit1c, fit2c, fit3c)
```


## fit_4c: k and delta ~ trt.  

```{r, eval=TRUE}
inits4 <- function() { list(
  b_Lmax=rnorm(1, 11.5, .25),
  b_Lmin=rnorm(1, 7.5, .25),
  b_delta=c(rexp(1, .5), 0, 0),
  b_k=c(rexp(1, 1), 0, 0),
  z_1=array(0, dim=c(72,1)),
  z_2=array(0, dim=c(72,1))
)
}

prior4 <- c(prior(normal(7.5,.25), nlpar="Lmin"),
            prior(normal(11.5, .25),nlpar="Lmax"),
            prior(exponential(1),nlpar="k"),
            prior(normal(0,0.02), nlpar="k", coef="trtWest"),
            prior(normal(0,0.02), nlpar="k", coef="trtWestHeat"),
            prior(exponential(0.5), nlpar="delta"), # 1 is exponential model
            prior(normal(0,0.25), nlpar="delta", coef="trtWest"),
            prior(normal(0,0.25), nlpar="delta", coef="trtWestHeat")
)

fit_4c <- brm(
  formula=bf(
    length2 | cens(censored) ~ Lmax - (Lmax - Lmin) * exp(-(k*hour)^delta), #Weibull model
    Lmax + Lmin ~ 1, 
    delta + k ~ trt + (1|id),   # 
    nl=TRUE ),
  data=style,
  prior=prior4,
  inits=inits4,
  cores=4,
  chains=4,
  iter=10000, control = list(adapt_delta=0.95)
) 

fit_4c <- add_criterion(fit_4c, "loo")

gc()
```

```{r}
summary(fit_4c)
gc()
```

```{r}
pairs(fit_4c, pars = "^b_")
```


```{r, fig.height=10}
plot(fit_4c, ask = FALSE)
gc()
```

```{r}
plot(conditional_effects(fit_4c), ask=FALSE)
pp_check(fit_4c)
```

```{r}
pred_4c <- predict(fit_4c)
pred_4c %>%
  cbind(style) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_smooth(span=1) +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_smooth(aes(y=Estimate), lty=2, span=1) 
```

```{r}
pred_4c %>%
  cbind(style) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_smooth(span=1) +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_smooth(aes(y=Estimate), lty=2, span=1)  +
  facet_wrap(~day, scales="free_y")
```


```{r}
pred_4c %>%
  cbind(style) %>%
  group_by(trt, hour) %>%
  summarize(length2 = mean(length2),
            Estimate = mean(Estimate)) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_line() +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_line(aes(y=Estimate), lty=2) 
```

```{r}
pred_4c %>%
  cbind(style) %>%
  group_by(day, trt, hour) %>%
  summarize(length2 = mean(length2),
            Estimate = mean(Estimate)) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_point() +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_line(aes(y=Estimate), lty=2) +
  facet_wrap(~day, scales = "free_y")
```

```{r}
loo_compare(fit1c, fit2c, fit3c, fit_4c)
```

```{r}
save.image(file="../output/models.Rdata")
```


## fit_5c: k + delta ~ trt + (1|id); Lmax ~ 1|day

```{r, eval=TRUE}
inits5 <- function() { list(
  b_Lmax=rnorm(1, 11.5, .25),
  b_Lmin=rnorm(1, 7.5, .25),
  b_delta=c(rexp(1, .5), 0, 0),
  b_k=c(rexp(1, 1), 0, 0),
  z_1=array(0, dim=c(8,1)),
  z_2=array(0, dim=c(72,1)),
  z_3=array(0, dim=c(72,1))
)
}

prior5 <- c(prior(normal(7.5,.25), nlpar="Lmin"),
            prior(normal(11.5, .25),nlpar="Lmax"),
            prior(exponential(1),nlpar="k"),
            prior(normal(0,0.02), nlpar="k", coef="trtWest"),
            prior(normal(0,0.02), nlpar="k", coef="trtWestHeat"),
            prior(exponential(0.5), nlpar="delta"), # 1 is exponential model
            prior(normal(0,0.25), nlpar="delta", coef="trtWest"),
            prior(normal(0,0.25), nlpar="delta", coef="trtWestHeat")
)

fit_5c <- brm(
  formula=bf(
    length2 | cens(censored) ~ Lmax - (Lmax - Lmin) * exp(-(k*hour)^delta), #Weibull model
    Lmin ~ 1, 
    Lmax ~ (1|day),
    delta + k ~ trt + (1|id),   # 
    nl=TRUE ),
  data=style,
  prior=prior5,
  sample_prior = "yes",
  inits=inits5,
  cores=4,
  chains=4,
  iter=2000
) 

fit_5c <- add_criterion(fit_5c, "loo")

gc()
```

```{r}
summary(fit_5c)
gc()
```

```{r, fig.height=10}
plot(fit_5c, ask = FALSE)
gc()
```

```{r}
plot(conditional_effects(fit_5c), ask=FALSE)
pp_check(fit_5c)
```

```{r}
pred_5c <- predict(fit_5c)
pred_5c %>%
  cbind(style) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_smooth(span=1) +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_smooth(aes(y=Estimate), lty=2, span=1) 
```

```{r}
pred_5c %>%
  cbind(style) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_smooth(span=1) +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_smooth(aes(y=Estimate), lty=2, span=1)  +
  facet_wrap(~day)
```


```{r}
pred_5c %>%
  cbind(style) %>%
  group_by(trt, hour) %>%
  summarize(length2 = mean(length2),
            Estimate = mean(Estimate)) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_line() +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_line(aes(y=Estimate), lty=2) 
```

```{r}
pred_5c %>%
  cbind(style) %>%
  group_by(day, trt, hour) %>%
  summarize(length2 = mean(length2),
            Estimate = mean(Estimate)) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_point() +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_line(aes(y=Estimate), lty=2) +
  facet_wrap(~day, scales = "free_y")
```

```{r}
loo_compare(fit1c, fit2c, fit3c, fit_4c, fit_5c)
```


## fit_6c:

```{r, eval=TRUE}

inits6 <- function() { list(
  b_Lmax=rnorm(1, 11.5, .25),
  b_Lmin=rnorm(1, 7.5, .25),
  b_delta=c(rexp(1, .5), 0, 0),
  b_k=c(rexp(1, 1), 0, 0),
  z_1=array(0, dim=c(8,1)),
  z_2=array(0, dim=c(8,1)),
  z_3=array(0, dim=c(72,1)),
  z_4=array(0, dim=c(72,1))
)
}

prior6 <- c(prior(normal(7.5,.25), nlpar="Lmin"),
            prior(normal(11.5, .25),nlpar="Lmax"),
            prior(exponential(1),nlpar="k"),
            prior(normal(0,0.04), nlpar="k", coef="trtWest"),
            prior(normal(0,0.04), nlpar="k", coef="trtWestHeat"),
            prior(exponential(0.5), nlpar="delta"), # 1 is exponential model
            prior(normal(0,0.25), nlpar="delta", coef="trtWest"),
            prior(normal(0,0.25), nlpar="delta", coef="trtWestHeat")
)

fit_6c <- brm(
  formula=bf(
    length2 | cens(censored) ~ Lmax - (Lmax - Lmin) * exp(-(k*hour)^delta), #Weibull model
    Lmax + Lmin ~ (1|day),
    delta + k ~ trt + (1|id),   # 
    nl=TRUE ),
  data=style,
  prior=prior6,
  sample_prior = "yes",
  inits=inits6,
  cores=4,
  chains=4,
  iter=2000
  )

fit_6c <- add_criterion(fit_6c, "loo")

gc()
```


```{r}
summary(fit_6c)
gc()
```

```{r, height=10}
plot(fit_6c, ask = FALSE)
gc()
```

```{r}
plot(conditional_effects(fit_6c), ask=FALSE)
pp_check(fit_6c)
```

```{r}
pred_6c <- predict(fit_6c) 
pred_6c %>%
  cbind(style) %>%
  ggplot(aes(x=hour, y=length2, color=trt)) +
  geom_smooth(span=1) +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_smooth(aes(y=Estimate), lty=2, span=1) 
```

```{r}
pred_6c %>%
  cbind(style) %>%
  ggplot(aes(x=hour, y=length, color=trt)) +
  geom_smooth(span=1) +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_smooth(aes(y=Estimate), lty=2, span=1)  +
  facet_wrap(~day, scales = "free_y")
```

```{r}
pred_6c %>%
  cbind(style) %>%
  group_by(day, trt, hour) %>%
  summarize(length = mean(length),
            Estimate = mean(Estimate)) %>%
  ggplot(aes(x=hour, y=length, color=trt)) +
  geom_point() +
  #geom_ribbon(aes(ymin=Q2.5, ymax=Q97.5), color="grey90", fill="black", alpha=.1) +
  geom_line(aes(y=Estimate), lty=2) +
  facet_wrap(~day, scales = "free_y", ncol = 4) +
  theme(legend.position = "top")
ggsave("../output/style_fit_plot.pdf", width=6.5, height = 4)
```

```{r}
save.image("../output/StyleModelFits.Rdata")
```


## compare models

```{r}
loo_compare(fit1c, fit2c, fit3c, fit_4c, fit_5c, fit_6c)
```


## posterior of best model

Get the posterior
```{r}
post_6c <- posterior_samples(fit_6c, pars="b.*")
```

posterior for inflection point
```{r}
# inflection point equation
infl.pt <- function(delta, k) {
  (1/k) *
    ((delta -1) / delta)^(1/delta)
}

post_6c$infl_intercept <- infl.pt(post_6c$b_delta_Intercept, post_6c$b_k_Intercept)

post_6c$infl_trtWest <-
  infl.pt(
    post_6c$b_delta_Intercept + post_6c$b_delta_trtWest,
    post_6c$b_k_Intercept + post_6c$b_k_trtWest)

post_6c$infl_trtWestHeat <-
  infl.pt(
    post_6c$b_delta_Intercept+post_6c$b_delta_trtWestHeat,
    post_6c$b_k_Intercept + post_6c$b_k_trtWestHeat)

```


```{r}
apply(post_6c, 2, function(x) mean(x))
```

posterior probability that inflection point for trtWestHeat is greater than inflection point for East
```{r}
sum( (post_6c$infl_trtWestHeat > post_6c$infl_intercept )) / nrow(post_6c)
```

posterior probability that inflection point for trtWest is greater than inflection point for East
```{r}
sum( (post_6c$infl_trtWest > post_6c$infl_intercept )) / nrow(post_6c)
```

posterior probability that inflection point for trtWest is greater than inflection point for trtWestHeat
```{r}
sum((post_6c$infl_trtWest > post_6c$infl_trtWestHeat)) / nrow(post_6c)
```

posterior probability that k for trtWestHeat is less than East
```{r}
sum( (post_6c$b_k_trtWestHeat < 0 )) / nrow(post_6c)
sum( (post_6c$b_k_trtWestHeat + post_6c$b_k_Intercept < post_6c$b_k_Intercept   )) / nrow(post_6c)
hypothesis(fit_6c, "k_trtWestHeat < 0")
```

posterior probability that k for trtWestHeat is less than East
```{r}
sum( (post_6c$b_k_trtWest < 0 )) / nrow(post_6c)
sum( (post_6c$b_k_trtWest + post_6c$b_k_Intercept < post_6c$b_k_Intercept   )) / nrow(post_6c)
```

### Plots

k
```{r, fig.width=3}
post_6c %>%
  as.data.frame() %>%
  select(starts_with("b_k")) %>%
  rename_with(~str_remove(.,"b_")) %>%
  rename_with(~str_remove(.,"trt")) %>%
  rename(k_East=k_Intercept) %>%
  mutate(k_West=k_West+k_East,
         k_WestHeat=k_WestHeat+k_East) %>%
  summarize(across(.fns = list(mean = mean,
                               lower = ~ rethinking::HPDI(., 0.95)[1],
                               upper = ~ rethinking::HPDI(., 0.95)[2])
                   )) %>%
  pivot_longer(cols=everything(), names_to=c("trt", "parameter"), names_pattern = "k_(.*)_(.*)") %>%
  pivot_wider(names_from = "parameter", values_from = "value") %>%
  ggplot(aes(x=trt, y=mean, ymin=lower, ymax=upper)) +
  geom_col(fill="skyblue") + 
  geom_errorbar(width=.5) +
  ylab("k") +
  xlab("Condition") +
  theme_bw()
ggsave("../output/style_k_plot.pdf", height=3, width = 3)
```
inflection
```{r, fig.width=3}
post_6c %>%
  as.data.frame() %>%
  select(starts_with("infl")) %>%
  rename_with(~str_remove(.,"trt")) %>%
  rename_with(~str_remove(.,"infl_")) %>%
  rename(East=intercept) %>%
  summarize(across(.fns = list(mean = mean,
                               lower = ~ rethinking::HPDI(., 0.95)[1],
                               upper = ~ rethinking::HPDI(., 0.95)[2])
                   )) %>%
  pivot_longer(cols=everything(), names_to=c("trt", "parameter"), names_pattern = "(.*)_(.*)") %>%
  pivot_wider(names_from = "parameter", values_from = "value") %>%
  ggplot(aes(x=trt, y=mean, ymin=lower, ymax=upper)) +
  geom_col(fill="red") + 
  geom_errorbar(width=.5) +
  ylab("Inflection Point") +
  xlab("Condition") +
  theme_bw()
ggsave("../output/style_inflection_plot.pdf", height=3, width = 3)
```



posterior probability that k for trtWest is less than k for trtWestHEat
```{r}
sum( (post_6c$b_k_trtWest < post_6c$b_k_trtWestHeat  )) / nrow(post_6c)
```
